A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-06-02 src/paper.tex
WIP: Introduction

Given the limitations of the conventional RC, a novel secondary screen architecture to identify viewers who are interacting with interactive TV (iTV) services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as secondary screens with the aim of capturing personal and contextualized interactions for each individual viewer in the iTV environment. By using proper machine learning algorithms, CPs can infer viewers' tastes from audience data in order to deliver personalized content~\cite{Kim2012,Shin2009}.

@@

% A range of Applications and iTV services can be developed to obtain the user ratings given to TV programs, amount of viewers, and user profiles. .

@@

As a potential alternative to handle the limitations of the RC, the proliferation of personal mobile devices has changed the people behavior towards audiovisual content consumption in interactive TV environments.

>>>>

Given the limitations of the conventional RC, a novel secondary screen architecture to identify viewers who are interacting with interactive TV (iTV) services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as secondary screens with the aim of capturing personal and contextualized interactions from each individual viewer in iTV environments. Thus, iTV applications and services can be developed to obtain viewers' interaction data. Examples of these applications include rating TV programs, amount of viewers, and user profiles.

By using proper machine learning algorithms, the captured data can reveal valuable information about viewers' tastes and behaviors~\cite{Kim2012,Shin2009}.

@@

@@
